---
title: "Asset Management PPP Loans"
knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})
author: "Adrian D. Garcia"
date: "July 2020"
output:
  html_document:
    toc: true
    toc_float: true
---

# Intro

## Getting Started

The goal of this project is to identify a list of firms within the asset management industry that received a PPP Loan from the Small Business Administration.

```{r setup, message = FALSE, warning = FALSE}

library(waffle) #Waffle graphs
library(tidyverse) #For Data Analysis
library(readxl)
library(lubridate) #For working with dates
library(DT) #For visualizing tables

```

First, I pull in the following data:

* SBA [data](https://sba.app.box.com/s/tvb0v5i57oa8gc6b5dcm9cyw7y2ms6pp). Pulled July 15, 2020. 661,218 rows and 16 columns.
* Morningstar Direct  mutual fund data. (I combined it using “Combine_Files.r”).  Pulled July 10, 2020. 25,569 rows and 11 columns.
* Morningstar Direct ETF data. Pulled July 22, 2020. 2,421 rows and 11 columns.
* SEC registered investment advisors [data](https://www.sec.gov/help/foiadocsinvafoiahtm.html). Pulled July 22, 2020. 13,647 rows and 262 columns.
* SEC exempt reporting advisors [data](https://www.sec.gov/help/foiadocsinvafoiahtm.html). Pulled July 22, 2020. 4,404 rows, 101 columns.
* FINRA regulated firm [data](https://www.finra.org/about/firms-we-regulate/0). Pulled July 22, 2020. 3,515 rows and 5 columns.

```{r load, message = FALSE, warning=FALSE}

SBA_Full <-
  read_csv("~/Data/ppp_loans/data/SBA/SBA_PPP_Data_071520.csv",
           guess_max = 25000)

MS_Full <-
  read_csv(
    "~/Data/ppp_loans/data/Morningstar/MS_Info_Report_071020_Full.csv",
    guess_max = 25000
  )

MS_ETF_Full <-
  read_csv(
    "~/Data/ppp_loans/data/Morningstar/MS_ETF_Report_072220_2421.csv",
    trim_ws = TRUE,
    guess_max = 2400,
    n_max = 
      nrow(read_csv("~/Data/ppp_loans/data/Morningstar/MS_ETF_Report_072220_2421.csv")) - 12
  )

SEC_RIA <-
  read_excel(
    "~/Data/ppp_loans/data/SEC/ia070120.xlsx",
    sheet = 1,
    guess_max = 13500
  )

SEC_Exempt <-
  read_excel(
    "~/Data/ppp_loans/data/SEC/ia070120-exempt.xlsx",
    sheet = 1,
    guess_max = 4400
  )

FINRA <-
  read_excel(
    "~/Data/ppp_loans/data/FINRA/FINRA_072220_IMPORTIO.xlsx",
    sheet = 1,
    guess_max = 3500
  )

```

Next, I make the following adjustments to the data sets.

* Replace spaces with periods in column names
* Limit some data
 + RIA: columns 1:26
 + Exempt: columns 1:25
 + FINRA: columns 2:4
* Combine Morningtar and ETF data
* Lowercase
 + **SBA_Adj**: BusinessName, Address, City, State
 + **MS_Adj**: Firm.Name, Firm..Street.Address, Advisor, Subadvisor
 + **SEC_RIA_Adj**: Primary.Business.Name, Legal.Name, Main.Office.Street.Address.1, Main.Office.Street.Address.2,Main.Office.City, Main.Office.State
 + **SEC_Adj**: Primary.Business.Name, Legal.Name, Main.Office.Street.Address.1, Main.Office.Street.Address.2,Main.Office.City, Main.Office.State
 + **FINRA**: Firm, Address, Mailing.Address
 * Modify **SBA_Adj** BusinessName names by removing punctuation ( _BusinessName.Mod_ ) and removing "llc", "inc", "llp", "co" and (ltd) ( _BusinessName.Mod1_ )

```{r adjustment, Message=FALSE}


MS_MF_Adj <- MS_Full %>%
  rename_all(make.names) %>%
  mutate(
    Firm.Name = tolower(Firm.Name),
    Firm..Street.Address = tolower(Firm..Street.Address),
    Advisor = tolower(Advisor),
    Subadvisor = tolower(Subadvisor),
    Pull = "Open end"
  )

MS_ETF_Adj <- MS_ETF_Full %>%
  rename_all(make.names) %>%
  mutate(
    Firm.Name = tolower(Firm.Name),
    Firm..Street.Address = tolower(Firm..Street.Address),
    Advisor = tolower(Advisor),
    Subadvisor = tolower(Subadvisor),
    Pull = "ETF"
  )

MS_Adj <- full_join(
  MS_MF_Adj,
  MS_ETF_Adj,
  by = c(
      "Name",
      "Firm.Name",
      "Firm..Street.Address",
      "Firm..Web.Address",
      "Advisor",
      "Subadvisor",
      "Manager.Name",
      "Manager.of.Managers",
      "Analyst.Name",
      "Master.Fund.Name",
      "Strategy.Name",
      "Pull"
    )
)

punct <- "[:punct:]+"
modifiers <- "[:space:](llc)?(inc)?(llp)?(co)?(lp)?(ltd)?$"

SBA_Adj <- SBA_Full %>%
  rename_all(make.names) %>%
  mutate(
    BusinessName = tolower(BusinessName),
    Address = tolower(Address),
    City = tolower(City),
    State = tolower(State),
    BusinessName.Mod = str_replace_all(BusinessName, punct, ""),
    BusinessName.Mod1 = str_replace_all(BusinessName.Mod, modifiers, "")
  )

SEC_RIA_Adj <- SEC_RIA %>%
  rename_all(make.names) %>%
  select(1:26) %>%
  mutate(
    Primary.Business.Name = tolower(Primary.Business.Name),
    Legal.Name = tolower(Legal.Name),
    Main.Office.Street.Address.1 = tolower(Main.Office.Street.Address.1),
    Main.Office.Street.Address.2 = tolower(Main.Office.Street.Address.2),
    Main.Office.City = tolower(Main.Office.City),
    Main.Office.State = tolower(Main.Office.State),
    TYPE = "RIA"
  )

SEC_Exempt_Adj <- SEC_Exempt %>%
  rename_all(make.names) %>%
  select(1:25) %>%
  mutate(
    Primary.Business.Name = tolower(Primary.Business.Name),
    Legal.Name = tolower(Legal.Name),
    Main.Office.Street.Address.1 = tolower(Main.Office.Street.Address.1),
    Main.Office.Street.Address.2 = tolower(Main.Office.Street.Address.2),
    Main.Office.City = tolower(Main.Office.City),
    Main.Office.State = tolower(Main.Office.State),
    TYPE = "EXEMPT"
  )

FINRA_Adj <- FINRA %>%
  rename_all(make.names) %>%
  mutate(
    Firm = tolower(New.column),
    Address = tolower(New.column..1.),
    Mailing.Address = tolower(New.column..2.)
  ) %>%
  select(6:8)

```

# SBA

The SBA data is categorized using NAICS codes. The [ones](https://www.naics.com/code-search/?naicstrms=mutual,fund) most relevant to us include:

* 523930, [investment advice](https://www.naics.com/code-search/?naicstrms=238990)
* 523920, portfolio management
* 523120, [securities brokerage](https://www.naics.com/code-search/?naicstrms=238990)
* 523999, [misc. financial investment activities](https://www.naics.com/code-search/?naicstrms=238990)
* 523110, [investment banking and securities dealing](https://www.naics.com/code-search/?naicstrms=238990)
* 541611, [Admin. management and general management consulting services](https://www.naics.com/code-search/?naicstrms=238990)
* 525910, open end investment funds
* 523130, securities brokerage
* 525990, other financial vehicles

```{r, sba, echo=TRUE}

SBA_Adj %>%
  group_by(NAICSCode) %>%
  summarise(Count = n()) %>%
  mutate(PCT = round(Count / sum(Count), 2) * 100) %>%
  arrange(desc(Count)) %>%
  filter(
    NAICSCode %in%
      c(
        "523930",
        "523920",
        "523120",
        "523999",
        "523110",
        "541611",
        "525910",
        "523130",
        "525990"
      ) |
      is.na(NAICSCode)
  ) %>%
  mutate(
    NAICSCode = case_when(
      is.na(NAICSCode) ~ "BLANK",
      TRUE ~ as.character(NAICSCode)
      ))%>% 
  datatable()

```


# Morningstar Mutual Funds

I want to start by seeing the firms, advisors and subadvisors within **MS_Adj** that mach companies in **SBA_Adj**

* Isolate distinct names for each category
* Modify names by removing punctuation
* Modify names by removing "llc", "inc", "llp", "co", "lp" and "ltd"

```{r MS_firms, Message=FALSE}

SBA_Firm <- SBA_Adj %>%
  distinct(BusinessName) %>% 
    mutate(
    BusinessName.Mod = str_replace_all(BusinessName, punct, ""),
    BusinessName.Mod1 = str_replace_all(BusinessName.Mod, modifiers, "")
  )

MS_Firm <- MS_Adj %>%
  group_by(Firm.Name,Firm..Street.Address) %>%
  summarise() %>% 
  mutate(
    Firm.Mod = str_replace_all(Firm.Name, punct, ""),
    Firm.Mod1 = str_replace_all(Firm.Mod, modifiers, ""),
    MS_Firm = "MS_Firm"
  )

MS_Advisor <- MS_Adj %>%
  distinct(Advisor) %>%
  mutate(
    Advisor.Mod = str_replace_all(Advisor, punct, ""),
    Advisor.Mod1 = str_replace_all(Advisor.Mod, modifiers, ""),
    MS_Advisor = "MS_Advisor"
  )

MS_Subadvisor <- MS_Adj %>%
  distinct(Subadvisor) %>%
  mutate(
    Subadvisor.Mod = str_replace_all(Subadvisor, punct, ""),
    Subadvisor.Mod1 = str_replace_all(Subadvisor.Mod, modifiers, ""),
    MS_Subadvisor = "MS_Subadvisor"
  )

```

102 mutual fund and ETF firms matched in the Morninstar datbase. There are some duplicates.

```{r, MF_firm_match, echo = FALSE}

MS_Firm %>%
  select(
    1,
    3,
    4
  ) %>% 
inner_join(., SBA_Firm, by= c("Firm.Mod1" = "BusinessName.Mod1")) %>% 
  datatable()

```

102 advisor firms in Morningstar match companies in the SBA dataset. Some of the matches are duplicates.

```{r, MF_advisor_match, echo = FALSE}

inner_join(MS_Advisor, SBA_Firm, by= c("Advisor.Mod1" = "BusinessName.Mod1")) %>% 
  datatable()

```

45 subadvisor firms in Morningstar match with companies in the SBA dataset.match just based on names. There are duplicates.

```{r, MF_subadvisor_match, echo = FALSE}

# inner_join(MS_Subadvisor, SBA_Firm, by= c("Subadvisor.Mod" = "BusinessName.Mod")) %>% 
#   datatable()
MS_Subadvisor %>%
  filter(
    !is.na(Subadvisor)
  ) %>% 
inner_join(., SBA_Firm, by= c("Subadvisor.Mod1" = "BusinessName.Mod1")) %>% 
  datatable()

```

# SEC DATA

I want to start by seeing the businesses within **SEC_Exempt_Adj** and **SEC_RIA_Adj** that mach companies in **SBA_Adj**
I can combine the files as **SEC_Adj**


* Isolate distinct names for each category
* Modify names by removing punctuation
* Modify names by removing "llc", "inc", "llp", and "co"

```{r, SEC, message = FALSE}

SEC_Adj <- 
  SEC_Exempt_Adj %>%
  group_by(
    Primary.Business.Name,
    Legal.Name,
    Main.Office.Street.Address.1,
    Main.Office.Street.Address.2,
    Main.Office.City,
    Main.Office.Postal.Code,
    TYPE) %>%
  summarise() %>% 
  full_join(
  .,
  SEC_RIA_Adj,
  by = c(
    "Primary.Business.Name",
    "Legal.Name",
    "Main.Office.Street.Address.1",
    "Main.Office.Street.Address.2",
    "Main.Office.City",
    "Main.Office.Postal.Code",
    "TYPE")
  )

SEC_BizName <- SEC_Adj %>%
  group_by(
    Primary.Business.Name,
    Main.Office.Street.Address.1,
    Main.Office.Street.Address.2,
    Main.Office.City,
    Main.Office.Postal.Code,
    TYPE
    ) %>%
  summarise() %>% 
  mutate(
    BizName.Mod = str_replace_all(Primary.Business.Name, punct, ""),
    BizName.Mod1 = str_replace_all(BizName.Mod, modifiers, ""),
    SEC_BizName = "SEC_BizName"
  )

SEC_LegalName <- SEC_Adj %>%
    group_by(
      Legal.Name,
      Main.Office.Street.Address.1,
      Main.Office.Street.Address.2,
      Main.Office.City,
      Main.Office.Postal.Code,
      TYPE
      ) %>%
 summarise() %>% 
  mutate(
    Legal.Name.Mod = str_replace_all(Legal.Name, punct, ""),
    Legal.Name.Mod1 = str_replace_all(Legal.Name.Mod, modifiers, ""),
    SEC_LegalName = "SEC_LegalName"
  )


# a <- MS_Adj %>%
#     mutate(
#         ZIP = str_extract(Firm..Street.Address, "(?<!box[:space:](\\d)?)\\d{5,}")
#     )

```

1,373 firms (exempt incl.) registered with SEC match with SBA data.

```{r, SEC_Biz_Match, echo = FALSE}

# inner_join(MS_Subadvisor, SBA_Firm, by= c("Subadvisor.Mod" = "BusinessName.Mod")) %>% 
#   datatable()

inner_join(SEC_BizName, SBA_Firm, by= c("BizName.Mod1" = "BusinessName.Mod1")) %>% 
  datatable()

```

1,484 firms (exempt incl.) registered with SEC match with SBA data.

```{r, SEC_Legal_Match, echo = FALSE}

# inner_join(MS_Subadvisor, SBA_Firm, by= c("Subadvisor.Mod" = "BusinessName.Mod")) %>% 
#   datatable()

inner_join(SEC_LegalName, SBA_Firm, by= c("Legal.Name.Mod1" = "BusinessName.Mod1")) %>% 
  datatable()

```

# FINRA

I want to start by seeing the businesses within **FINRA_Adj** that mach companies in **SBA_Adj**

* Isolate distinct names for each category
* Modify names by removing punctuation
* Modify names by removing "llc", "inc", "llp", and "co"

```{r, finra_firms, message=FALSE}

FINRA_Firm <- FINRA_Adj %>%
  group_by(Firm, Address) %>%
  summarise() %>% 
  mutate(
    Firm.Mod = str_replace_all(Firm, punct, ""),
    Firm.Mod1 = str_replace_all(Firm.Mod, "[:space:](llc)?(inc)?(llp)?(co)??(ltd)?$", ""),
    FINRA_Firm = "FINRA_Firm"
  )

```

355 firms regulated by FINRA match.

```{r, Finra_Match, echo = FALSE}

# inner_join(MS_Subadvisor, SBA_Firm, by= c("Subadvisor.Mod" = "BusinessName.Mod")) %>% 
#   datatable()

inner_join(FINRA_Firm, SBA_Firm, by= c("Firm.Mod1" = "BusinessName.Mod1")) %>% 
  datatable()

```

# Results

```{r, results, message=FALSE}

Matches <- SBA_Adj %>% 
  filter(BusinessName.Mod1 %in% MS_Firm$Firm.Mod1 |
          BusinessName.Mod1 %in% MS_Advisor$Advisor.Mod1 |
           BusinessName.Mod1 %in% MS_Subadvisor$Subadvisor.Mod1 |
           BusinessName.Mod1 %in% SEC_BizName$BizName.Mod1 |
           BusinessName.Mod1 %in% SEC_LegalName$Legal.Name.Mod1
         )

write_csv(Matches, "matching_names_SBA.csv")

Paired <-
  left_join(
    Matches,
    MS_Firm,
    by = c(
      "BusinessName.Mod1" = "Firm.Mod1"
    )
  ) %>%
  left_join(
    .,
    MS_Advisor,
    by = c(
      "BusinessName.Mod1" = "Advisor.Mod1"
    )
  ) %>%
  left_join(
    .,
    MS_Subadvisor, 
    by = c(
      "BusinessName.Mod1" = "Subadvisor.Mod1"
      )
    ) %>%
  left_join(.,
            SEC_BizName,
            by = c(
              "BusinessName.Mod1" = "BizName.Mod1"
              )
            ) %>%
  left_join(
    .,
    SEC_LegalName,
    by = c(
      "BusinessName.Mod1" = "Legal.Name.Mod1"
    )
  )

write_csv(Paired, "paired_SBA.csv")

```

We have 1,631 matches.

The SBA data is categorized using NAICS codes. The [ones](https://www.naics.com/code-search/?naicstrms=mutual,fund) most relevant to us include:

* 523930, [investment advice](https://www.naics.com/code-search/?naicstrms=238990)
* 523920, portfolio management
* 523120, [securities brokerage](https://www.naics.com/code-search/?naicstrms=238990)
* 523999, [misc. financial investment activities](https://www.naics.com/code-search/?naicstrms=238990)
* 523110, [investment banking and securities dealing](https://www.naics.com/code-search/?naicstrms=238990)
* 541611, [Admin. management and general management consulting services](https://www.naics.com/code-search/?naicstrms=238990)
* 525910, open end investment funds
* 523130, securities brokerage
* 525990, other financial vehicles

```{r, results_show, echo=FALSE}

Matches %>% 
  group_by(NAICSCode) %>% 
  summarise(Count = n()) %>% 
  arrange(desc(Count)) %>%
  datatable()

```